How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-05-19 Draft_May_2022/Full_draft_20220510.rmd
Some more changes to code in files

---
title: How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985
author:
- Livio Silva-Muller
- Henrique Sposito^[Both co-authors contributed equally to the article; names are ordered alphabetically. Both of them are PhD candidates at The Geneva Graduate Institute. Livio is affiliated to the Albert Hirschman Centre on Democracy. Henrique is affiliated to the Centre for International Environmental Studies.]
date: "May 2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document:
    reference_docx: template.docx
always_allow_html: TRUE
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon Rainforest is one of the most important ecosystems in the world, and most of this biome is located in Brazil. Albeit the importance of understanding the relationship between the social construction of the Amazon and its effects on environmental outcomes, we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments. Discursive problem-construction within democracies legitimize ways of thinking and acting towards the environment while affecting decisions to deforest, or not, at the local level. Building on Hirschman’s conceptualization of chosen problems (1963), we propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in political discourse. Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in 6130 official presidential speeches since 1985. We find that, first, international environmental events appear to drive presidents to speak more about the Amazon. Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015. Constructing the Amazon as an issue of sovereignty also became more pertinent from 2010 onwards. Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
---

@@

@@

        legend.position = "bottom") +
  annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.35,
           fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
                    "grey50", "ghostwhite", "grey50", "ghostwhite"),
           alpha = 0.1) +
  annotate(geom = "text", x = hp$label, y = 0.04, vjust = 0.3,
           label = hp$presid, alpha = 0.4)

@@

adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))

>>>>

---
title: How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985
author:
- Livio Silva-Muller
- Henrique Sposito^[Both co-authors contributed equally to the article; names are ordered alphabetically. Both of them are PhD candidates at The Geneva Graduate Institute. Livio is a PhD Candidate in Anthropology and Sociology at the Geneva Graduate Instituteis affiliated to the Albert Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations and Political Sciences at the Geneva Graduate Institute affiliated to the Centre for International Environmental Studies.]
date: "May 2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document:
    reference_docx: template.docx
always_allow_html: TRUE
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon Rainforest is one of the most important ecosystems in the world, and most of this biome is located in Brazil. Albeit the importance of understanding the relationship between the social construction of the Amazon and its effects on environmental outcomes, we lack empirical accounts of how the Brazilian Amazon has been constructed as a problem in discourses over time, by geographical location, and between, or within, governments. Discursive problem-construction within democracies legitimize ways of thinking and acting towards the environment while affecting decisions to deforest, or not, at the local level. Building on Hirschman’s conceptualization of chosen problems (1963), we propose a framework to investigate how the Brazilian Amazon has been constructed as a problem in political discourse. Combining hand-coding and supervised machine learning, we classify statements about the Amazon forest or region in 6130 official presidential speeches since 1985. We find that, first, international environmental events appear to drive presidents to speak more about the Amazon. Second, while the Amazon as a problem of economic integration dominated discourses from 1985 to the mid-2000s, environmental conservation and social development constructions briefly surpasses economic integration from 2010 to 2015. Constructing the Amazon as an issue of sovereignty also became more pertinent from 2010 onwards. Finally, using a multinomial regression model, we find that presidents are more likely to construct the Amazon as a problem of environmental conservation, than economic integration or social development, as presidents move away from the Amazon region.
---

@@

adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050)) # Missing year data

@@

        legend.position = "bottom")
# # Same plot but annotated
# Amazon_year <- perc1 %>% ggplot(., aes(x = year, y = perc)) +
#   geom_line(color = "darkgreen") +
#         legend.position = "bottom") +
#   annotate(geom = "rect", xmin = hp$beg, xmax = hp$end, ymin = 0, ymax = 0.35,
#            fill = c("grey50", "ghostwhite", "grey50", "ghostwhite",
#                     "grey50", "ghostwhite", "grey50", "ghostwhite"),
#            alpha = 0.1) +
#   annotate(geom = "text", x = hp$label, y = 0.04, vjust = 0.3,
#            label = hp$presid, alpha = 0.4) +
#   annotate(geom = "segment", x = amazon_def_year$year, y = amazon_def_year$def_year)

@@
